Topological Equivariant Artist Model

### 2022-01-26 slides/main.tex
graphic bundle
sheaves

                \item[\textcolor{total}{Graphic \gtotalc}]{virtual rendered output}
                \item[\textcolor{base}{Continuity \gbasec}]{topology of graphic in rendered space}
                \item[\textcolor{fiber}{Display \gfiberc}] {generalization of renderer specifications, e.g. \{xy,rgba\}, \{xy, cymk\}, \{xyz, rgba\}}

@@

\begin{frame}{Sheaves} 
    A sheaf is a presheaf that satisfies the following two axioms\cite{bakerMathsSheaf}\\
    \begin{block}<2-|handout:1>{locality}
        if there exists the open covering $\mathcal{\opensetc} = \{\opensetc_i\}_{i\in I}$ of \opensetc
        \onslide<3-|handout:1>{
        and if $\dsectionc^{a}, \dsectionc^{b} \in \sheafc(\opensetc_i)$ have the property $\dsectionc^{a}\restriction_{\opensetc_i} = \dsectionc^{b}\restriction_{\opensetc_i}$ for each $\opensetc_i \in \mathcal{\opensetc}$,}
        \onslide<4|handout:1>{ then $\dsectionc^{a} = \dsectionc^{b}$}
    \end{block} 
    \begin{block}<5-|handout:1>{gluing} 
        if there exists the open covering $\mathcal{\opensetc} = \{\opensetc_i\}_{i\in I}$ of \opensetc\ and if $\dsectionc^{i} \in \sheafc(\opensetc_i)$ is given for each $i \in I$
        \onslide<6-|handout:1>{such that ${\dsectionc^{i}}\restriction_{\opensetc_i\cap \opensetc_j} = {\dsectionc^{j}}\restriction_{\opensetc_i \cap \opensetc_j}$ for each pair $\opensetc_i, \opensetc_j \in \mathcal{\opensetc}$,}
        \onslide<7-|handout:1>{ then there exists $\dsectionc \in \sheafc(\opensetc)$ such that $\dsectionc\restriction_{\opensetc_i} = {\dsectionc^{i}}$ for each $i \in I$} 
    \end{block}      
\end{frame}

>>>>

                \item[\textcolor{total}{Graphic \gtotalc}]{continuity + renderer fields}
                \item[\textcolor{base}{Continuity \gbasec}]{parameterization of the graphic's geometry}
                \item[\textcolor{fiber}{Display \gfiberc}] {renderer fields, e.g. \{xy,rgba\}, \{xy, cymk\}, \{xyz, rgba\}}

@@

\begin{frame}{Sheaves} 
    A sheaf is a presheaf that satisfies the following two axioms\cite{bakerMathsSheaf}\\
    \begin{block}<2-|handout:1>{locality}
        \onslide<3-|handout:1>{
        given $\opensetc = \bigcup\limits_{i\in I} \opensetc_i$ and $\dsectionc^{a}, \dsectionc^{b} \in \sheafc(\opensetc)$,}
        \onslide<4|handout:1>{\\
        if $\dsectionc^{a}\restriction_{\opensetc_i} = \dsectionc^{b}\restriction_{\opensetc_i}$ for each $\opensetc_i \in \opensetc$}
        \onslide<4|handout:1>{then $\dsectionc^{a} = \dsectionc^{b}$}
    \end{block} 
    \begin{block}<5-|handout:1>{gluing} 
         given $\dsectionc^{i} \in \sheafc(\opensetc_i)$
        \onslide<6-|handout:1>{s.t. ${\dsectionc^{i}}\restriction_{\opensetc_i\cap \opensetc_j} = {\dsectionc^{j}}\restriction_{\opensetc_i \cap \opensetc_j}$ for $\opensetc_i, \opensetc_j \in \opensetc$,}
        \onslide<7-|handout:1>{\\there exists $\dsectionc \in \sheafc(\opensetc)$ such that $\dsectionc\restriction_{\opensetc_i} = {\dsectionc^{i}}$} 
    \end{block}      
\end{frame}
